Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-02 paper/structureScene.tex
Edit feature design section

Before constructing models for classification or similarity estimation, it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review two transformations which achieve these properties, namely logarithmic compression and standardization.

@@

For the task of musical genre recognition, second-order scattering coefficients $\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2)$ are sometimes normalized by the corresponding first-order scattering coefficients $\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)$, since this decorrelates them from one another \cite{Anden2014}.
We note that taking the logarithm of such renormalized coefficients yields
\begin{equation}
\log \dfrac{\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2)}{\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)} =
\log \mathbf{S_2}\boldsymbol{x}(t, \gamma_1, \gamma_2) -
\log \mathbf{S_1}\boldsymbol{x}(t, \gamma_1),
\end{equation}
\ie a linear combination of the logarithms of first- and second-order coefficients.
As such, a nonlinear renormalization becomes a linear transformation, which can be learned by a linearly discriminative classifier.

\subsection{Standardization}
\label{sec:stand}

Let $\mathbf{S}\boldsymbol{x}(\gamma,n)$ be a dataset, where the $\gamma$ and $n$ respectively denotes feature and sample indices, respectively.
It has been found that SVMs should be trained on scaled features with null mean and unit variance so as to avoid mismatch in numeric ranges \cite{Hsu2003}.
To standardize $\mathbf{S}\boldsymbol{x}(\gamma,n)$, we subtract the sample mean vector $\mu[\mathbf{S}\boldsymbol{x}(\gamma)]$ from $\mathbf{S}\boldsymbol{x}(\gamma,n)$ and divide the result by the sample standard deviation vector $\sigma[\mathbf{S}\boldsymbol{x}] (\gamma)$.
The vectors $\mu[\mathbf{S}\boldsymbol{x}(\gamma)]$ and $\sigma[\mathbf{S}\boldsymbol{x}](\gamma)$ are estimated from the training set only, and the same affine transformation is then applied to all samples in both the training and the test sets.

>>>>

Before constructing models for similarity estimation, it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review two transformations which achieve these properties: logarithmic compression and standardisation.

@@

\subsection{Standardisation}
\label{sec:stand}

Let $\mathbf{S}\boldsymbol{x}(\gamma,n)$ be a dataset, where $\gamma$ and $n$ denote feature and sample indices, respectively.
Many algorithms operate better on features which have zero mean and unit variance to avoid mismatch in numeric ranges \cite{Hsu2003}.
To standardise $\mathbf{S}\boldsymbol{x}(\gamma,n)$, we subtract the sample mean vector $\mu[\mathbf{S}\boldsymbol{x}(\gamma)]$ from $\mathbf{S}\boldsymbol{x}(\gamma,n)$ and divide the result by the sample standard deviation vector $\sigma[\mathbf{S}\boldsymbol{x}] (\gamma)$.
The vectors $\mu[\mathbf{S}\boldsymbol{x}(\gamma)]$ and $\sigma[\mathbf{S}\boldsymbol{x}](\gamma)$ are estimated from the entire dataset.
